---
title: "Nr6a1 down elements in ATAC"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Exploring elements that were mis-regulated by Nr6a1 overexpression 

```{r message=FALSE}

rm(list=ls())
library(RColorBrewer)
library(tidyverse)
library(ComplexHeatmap)


```
### Load settings

Colors, main directory 

```{r}

source('./r_inputs/TemporalSpatialNeuralTube_settings.R')

```
### Set dirs

```{r}

subworkinput="inputs_glialnr6a1_3/"
outdir="outputs_glialnr6a1_3/"
ifelse(!dir.exists(file.path(workingdir,outdir)), dir.create(file.path(workingdir,outdir)), "Directory exists")

```

## Load data

BED tables from previous script intersected with the CaTS ATAC consensus to find the consensus elements and plot their accessibility. 

Counts/vsd from full GLIAL ATAC

```{r }

#counts table
count_atac <- read.table(file = paste0(workingdir,"outputs_glialatac_1/","consensus_peaks.mLb.clN.normCounts.txt"),header=TRUE, stringsAsFactors = FALSE)
vsd_atac <- read.csv(file=paste0(workingdir,"outputs_glialatac_1/","consensus_peaks.mLb.vsd.csv"),header=TRUE, stringsAsFactors = FALSE)


## Annotation table
ann_table <- read.table(file=paste0(workingdir,"inputs_glialatac_1_eda_pca/","consensus_peaks.mLb.clN.annotatePeaks.txt"), header=TRUE, stringsAsFactors = FALSE, sep = "\t")
colnames(ann_table)[1] <- "Peakid"


ann_table_clean <- ann_table %>% 
  select(c("Peakid","Chr","Start","End","Strand","Annotation","Distance.to.TSS","Nearest.PromoterID")) %>%
  separate(Annotation, into = "Annotation_brief", sep = " ", remove = FALSE)

```


```{r}

nr6a1down_elements <- read.table(file = paste0(workingdir,subworkinput,"Nr6a1_down__within__consensus.bed"),header=FALSE, stringsAsFactors = FALSE)

nr6a1down_elements_ann <- nr6a1down_elements %>% 
  left_join(ann_table_clean, by=c("V4"="Peakid"))

```


## Make ave per condition 

For the subset of elements

```{r}
## make averages by condition

vsd_sub <- vsd_atac %>%
  filter(X %in% nr6a1down_elements$V4) %>%
  pivot_longer(values_to = "vsd", names_to = "sampleid", MUT_D7_pM_NFIAn_R1:WT_D9_p2_NFIAn_R1) %>%
  separate(sampleid, into = c("geno","day","gate","nfia","rep")) %>%
  mutate(condition=paste(geno,day,gate, sep="_")) %>%
  group_by(X,condition) %>%
  summarise(vsd_ave=mean(vsd)) %>%
  pivot_wider(values_from = vsd_ave, names_from = condition)

```



## Plot original ATAC for this subset of elements


```{r fig.width=5, fig.height=4}
# make a heatmap of CaTS-RNA: this heatmap filters rows of genes with sd zero
# filter genes
vsd_hm <- vsd_sub %>%
  column_to_rownames("X") %>%
  select(starts_with("WT"))

dim(vsd_hm)

vsd_hm_z <- t(scale(t(vsd_hm))) 

# order the columns
vsd_hm_z <- vsd_hm_z[,sorted_WTDayGate]

# metadata for the heatmap
genecolData_first <- data.frame(Sample_ID = colnames(vsd_hm_z))
genecolData_first <- genecolData_first %>% 
  separate(Sample_ID,into=c("Genotype","Day","Gate"), sep="_", remove=FALSE) %>%
  mutate(DayGate=paste(Day,Gate,sep="_"))
genecolData_first <- as.data.frame(unclass(genecolData_first))

phen_data <- genecolData_first %>%
  select(c("Sample_ID","DayGate","Day")) %>%
  remove_rownames() %>%
  column_to_rownames("Sample_ID")

ann_color_JD <- list(
  DayGate = c(D5_p1="#abdff4",D5_p2="#f1df9a", D5_pM="#f19aac",
              D7_p1="#55bee8",D7_p2="#e6c444",D7_pM="#e64466",
              D9_p1="#1a91c1",D9_p2="#c19e1a",D9_pM="#c11a3d",
              D11_p1="#0e506b",D11_p2="#6b570e",D11_pM="#7c1127"),
  Day = c(D5="#fadede",D7="#f3aaaa",D9="#e96666",D11="#cf1e1e"))

# Build the annotation for the complex heatmap
colAnn <- HeatmapAnnotation(
    df = phen_data,
    which = 'col', # 'col' (samples) or 'row' (gene) annotation?
    na_col = 'white', # default colour for any NA values in the annotation data-frame, 'ann'
    col = ann_color_JD,
    annotation_height = 0.6,
    annotation_width = unit(1, 'cm'),
    gap = unit(1, 'mm'))

# Annotated heatmap with selected colors
hm_colors = colorRampPalette(rev(brewer.pal(n = 11, name = "RdBu")))(100)


hmap_catsATAC <- Heatmap(vsd_hm_z,
    name = 'Z-score',

    col = hm_colors,

    # row (gene) parameters
      cluster_rows = TRUE,
      show_row_dend = TRUE,
      #row_title = 'Statistically significant genes',
      row_title_side = 'left',
      row_title_gp = gpar(fontsize = 12,  fontface = 'bold'),
      row_title_rot = 90,
      show_row_names = FALSE,
      row_names_gp = gpar(fontsize = 12, fontface = 'bold'),
      row_names_side = 'left',
      row_dend_width = unit(25,'mm'),

    # column (sample) parameters
      cluster_columns = FALSE,
      show_column_dend = TRUE,
      column_title = '',
      column_title_side = 'bottom',
      column_title_gp = gpar(fontsize = 12, fontface = 'bold'),
      column_title_rot = 0,
      show_column_names = FALSE,
      column_names_gp = gpar(fontsize = 8),
      column_names_max_height = unit(10, 'cm'),
      column_dend_height = unit(25,'mm'),

    # cluster methods for rows and columns
      clustering_distance_columns = function(x) as.dist(1 - cor(t(x))),
      clustering_method_columns = 'ward.D2',
      clustering_distance_rows = function(x) as.dist(1 - cor(t(x))),
      clustering_method_rows = 'ward.D2',

    # specify top and bottom annotations
      top_annotation = colAnn)


 
draw(hmap_catsATAC,
    heatmap_legend_side = 'left',
    annotation_legend_side = 'left',
    row_sub_title_side = 'left')

# print heatmap
pdf(paste0(workingdir,outdir,"Heatmap_Nr6a1down_elements_in_CaTSATAC.pdf"), width = 10, height = 2) 

draw(hmap_catsATAC,
    heatmap_legend_side = 'left',
    annotation_legend_side = 'left',
    row_sub_title_side = 'left')

dev.off()

```

```{r}
sessionInfo()
```
