---
title: "RNA_2_time_vs_domain"
output: github_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

```

# RNA analysis
Differential accessibility in groups of samples

Generate the comparison and export the data. 

Start the analysis in the next script by importing these data so it is more efficient. 

```{r message=FALSE}

rm(list=ls())

library(DESeq2)
library(RColorBrewer)
library(ComplexHeatmap)
library(tximport)
library(tidyverse)

```

### Load settings

Colors, main directory 

```{r}

source('./r_inputs/TemporalSpatialNeuralTube_settings.R')

```


### Set dirs
```{r}

outdir="outputs_glialrna_2_time_space/"
subworkinput="inputs_glialRNA_1_qc/"
ifelse(!dir.exists(file.path(workingdir,outdir)), dir.create(file.path(workingdir,outdir)), "Directory exists")

suboutdir1="output_Domain_Specific/"
ifelse(!dir.exists(file.path(workingdir,outdir,suboutdir1)), dir.create(file.path(workingdir,outdir,suboutdir1)), "Directory exists")
suboutdir2="output_Time_Specific/"
ifelse(!dir.exists(file.path(workingdir,outdir,suboutdir2)), dir.create(file.path(workingdir,outdir,suboutdir2)), "Directory exists")


```



## Load data

For RNA analysis, we are using the output of star_salmon from `nf-core rnaseq`. Pipeline outpout directory: `results/star_salmon`

```{r }

#salmon counts from pipeline, import
path_files =  list.files(paste0(workingdir,subworkinput)) 
samples = data.frame(run=path_files, stringsAsFactors = FALSE) %>%
  filter(str_detect(run, "MUT|WT"))

files <- file.path(paste0(workingdir,subworkinput), samples$run, "quant.sf")
names(files) <- samples$run
all(file.exists(files))

#from pipeline
tx2gene = read_tsv(paste0(paste0(workingdir,subworkinput),"/salmon_tx2gene.tsv"))

txi.salmon <- tximport(files, type = "salmon", tx2gene = tx2gene)
#head(txi.salmon$counts)



```


## Differential analysis between domains for each timepoint

Targeted diff analysis in subsets of samples:

Wild type only:
D5: pairwise for p1, p2, pMN
D7: pairwise for p1, p2, pMN
D9: pairwise for p1, p2, pMN
D11: pairwise for p1, p2, pMN

Warning in DESeqDataSet(se, design = design, ignoreRank) : some variables in design formula are characters, converting to factors
## It is an expected warning because the R script change the type of the data from vectors to factors.

This DESeq2 analysis is done by subsetting samples. I subset the `txi.salmon$counts` table and then use ` DESeqDataSetFromMatrix` with `round(sub_counts)` to perform the differential analysis. 

```{r}

count_table <- txi.salmon$counts

count_matrix <- count_table %>%
  as.data.frame() %>%
  rownames_to_column("GeneID") %>%
  filter(!str_starts(GeneID, "ERCC")) %>%
  column_to_rownames("GeneID")


#subset 
timepoint=c("_D5_","_D7_","_D9_","_D11_")
#matrix
allgates=matrix(c("_pM_","_p2_","_pM_","_p1_","_p1_","_p2_"),
                 nrow=2,
                 ncol=3)
geno="WT_"

comparisons <- allgates

# count_matrix <- count_table %>%
#   column_to_rownames("Geneid")


PairWiseDEseq <- lapply(c(1:length(timepoint)),function (x) {
  lapply(c(1:ncol(allgates)), function (y) {
      timepoints <- timepoint[x]
      celltypes <- allgates[,y]
      sub_counts <- count_matrix %>%
        dplyr::select(starts_with(geno)  & contains(celltypes) & contains(timepoints))
      
      ## Make metadata file for DESeq
      genecolData_sub <- data.frame(Sample_ID = colnames(sub_counts))
      genecolData_sub <- genecolData_sub %>% 
        separate(Sample_ID,into=c("Genotype","Day","Gate","NFIAgate","Rep"), sep="_", remove=FALSE) %>%
        mutate(Condition=paste(Genotype,Day,Gate,NFIAgate, sep="_"),
         DayNFIA=paste(Day,NFIAgate,Genotype,sep = "_"),
         DayGate=paste(Day,Gate,sep="_"),
         Experiment=paste(Genotype,Rep,sep="_"),
         NFIAstatus=paste(NFIAgate,Genotype,sep="_"),
         Gate=factor(Gate, levels = gates))
      genecolData_sub <- as.data.frame(unclass(genecolData_sub))
      
      
      dds_sub <- DESeqDataSetFromMatrix(countData =  round(sub_counts),
                              colData = genecolData_sub,
                              design = ~ Gate)
          
      dds_sub <- DESeq(dds_sub)
      
      vsd_sub <- varianceStabilizingTransformation(dds_sub,blind = FALSE)
      
      # Export normalized tables for plotting elsewhere
      dds_sub_counts <- counts(dds_sub, normalized = TRUE)
      vsd_sub_data <- assay(vsd_sub)
      
      results_sub <- results(dds_sub)

      # plotMA(results_sub,ylim=c(-8,8))

      ## Export files
      
      write.table(dds_sub_counts,
      file = paste0(workingdir,outdir,suboutdir1,"CountsNormalized_",timepoints,resultsNames(dds_sub)[2],".txt"),
          quote = FALSE, row.names = TRUE)
      write.csv(vsd_sub_data,
          paste0(workingdir,outdir,suboutdir1,"VSData_",timepoints,resultsNames(dds_sub)[2],".csv"),
          quote = FALSE)
      write.table(results_sub,
          file = paste0(workingdir,outdir,suboutdir1,"Results_DESeq_",timepoints,resultsNames(dds_sub)[2],".txt"),
          quote = FALSE, row.names = TRUE)

      results_return <- results_sub %>% as.data.frame() %>% rownames_to_column("Geneid")
      results_return$Comparison <- paste0("Comp_",timepoints,resultsNames(dds_sub)[2])
      results_return

  })
}) 


```

## Differential analysis between timepoints for each domain

Targeted diff analysis in subsets of samples:

Wild type only:
p1: pairwise D5-D7, D7-D9, D9-D11, D5-D9, D5-D11, D7-D11
p2: pairwise D5-D7, D7-D9, D9-D11, D5-D9, D5-D11, D7-D11
pM: pairwise D5-D7, D7-D9, D9-D11, D5-D9, D5-D11, D7-D11

```{r}

#subset 
allgates=c("_p2_","_pM_","_p1_")
#matrix
timepoints=matrix(c("_D5_","_D7_","_D7_","_D9_","_D9_","_D11_","_D5_","_D9_","_D5_","_D11_","_D7_","_D11_"),
                 nrow=2,
                 ncol=6)
geno="WT_"

comparisons <- timepoints


PairWiseDEseq <- lapply(c(1:length(allgates)),function (x) {
  lapply(c(1:ncol(timepoints)), function (y) {
      celltypes <- allgates[x]
      days <- timepoints[,y]
      sub_counts <- count_matrix %>%
        dplyr::select(starts_with(geno)  & contains(celltypes) & contains(days))
      
      ## Make metadata file for DESeq
      genecolData_sub <- data.frame(Sample_ID = colnames(sub_counts))
      genecolData_sub <- genecolData_sub %>% 
        separate(Sample_ID,into=c("Genotype","Day","Gate","NFIAgate","Rep"), sep="_", remove=FALSE) %>%
        mutate(Condition=paste(Genotype,Day,Gate,NFIAgate, sep="_"),
         DayNFIA=paste(Day,NFIAgate,Genotype,sep = "_"),
         DayGate=paste(Day,Gate,sep="_"),
         Experiment=paste(Genotype,Rep,sep="_"),
         NFIAstatus=paste(NFIAgate,Genotype,sep="_"))
      genecolData_sub <- as.data.frame(unclass(genecolData_sub))
      
      dds_sub <- DESeqDataSetFromMatrix(countData = round(sub_counts),
                                    colData = genecolData_sub,
                                    design = ~ Day)
      
      dds_sub <- DESeq(dds_sub)
      
      vsd_sub <- varianceStabilizingTransformation(dds_sub,blind = FALSE)
      
      # Export normalized tables for plotting elsewhere
      dds_sub_counts <- counts(dds_sub, normalized = TRUE)
      vsd_sub_data <- assay(vsd_sub)
      
      results_sub <- results(dds_sub)

      #plotMA(results_sub,ylim=c(-8,8))

      ## Export files
      
      write.table(dds_sub_counts,
      file = paste0(workingdir,outdir,suboutdir2,"CountsNormalized_",celltypes,resultsNames(dds_sub)[2],".txt"),
          quote = FALSE, row.names = TRUE)
      write.csv(vsd_sub_data,
          paste0(workingdir,outdir,suboutdir2,"VSData_",celltypes,resultsNames(dds_sub)[2],".csv"),
          quote = FALSE)
      write.table(results_sub,
          file = paste0(workingdir,outdir,suboutdir2,"Results_DESeq_",celltypes,resultsNames(dds_sub)[2],".txt"),
          quote = FALSE, row.names = TRUE)

      results_return <- results_sub %>% as.data.frame() %>% rownames_to_column("Geneid")
      results_return$Comparison <- paste0("Comp_",celltypes,resultsNames(dds_sub)[2])
      results_return

  })
}) 


```





```{r}
sessionInfo()
```