---
title: "ATAC_3_temporal clusters"
output: github_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

```

# ATAC analysis


```{r message=FALSE}

rm(list=ls())

library(DESeq2)
library(RColorBrewer)
library(tidyverse)
library(ComplexHeatmap)
library(factoextra)
library(ggrepel)

```


### Load settings

Colors, main directory 

```{r}

source('./r_inputs/TemporalSpatialNeuralTube_settings.R')

```


### Set dirs
```{r}

subworkinput="outputs_glialatac_2_time_space/"
suboutdir2="output_Space_Specific/"

outdir="outputs_glialatac_3_timewt_kmeans/"
ifelse(!dir.exists(file.path(workingdir,outdir)), dir.create(file.path(workingdir,outdir)), "Directory exists")



```



## Load data

Load the diff expression from previous script. 



## Load vsd to plot heatmaps later
```{r load-vsd}

count_vsd <- read.csv(file=paste0(workingdir,"outputs_glialatac_1/","consensus_peaks.mLb.vsd.csv"),header=TRUE, stringsAsFactors = FALSE)


```


re importing does not work because the ~/ gets converted to full name of the dir

Change working dir to local and it'll be fine. For not, this is the patch. 

## Differential analysis between timepoints for each domain

Targeted diff analysis in subsets of samples:

Wild type only:
p1: pairwise D5-D7, D7-D9, D9-D11, D5-D9, D5-D11, D7-D11
p2: pairwise D5-D7, D7-D9, D9-D11, D5-D9, D5-D11, D7-D11
pM: pairwise D5-D7, D7-D9, D9-D11, D5-D9, D5-D11, D7-D11

```{r}

PairWiseDEseq_days <- lapply(list.files(path=paste0(workingdir,subworkinput,suboutdir2),pattern="Results_DESeq*", full.names=TRUE),function(x) {
  data <- read.table(x,header=T,stringsAsFactors=F) %>% as.data.frame() %>% rownames_to_column("Intervals")
  data$Comparison <- gsub(paste0("/Users/delasj/Dropbox \\(The Francis Crick\\)/Glial_cisReg/",subworkinput,suboutdir2,"/Results_DESeq_"),"", x)
  data$Comparison <- gsub(".txt","",data$Comparison)
  data
})

results_deseq_days <- do.call(rbind,PairWiseDEseq_days)

```


### How many diff acc elements between timepoints?

```{r filter-days}

top_days_comparisons <- results_deseq_days %>%
  as.data.frame() %>%
  filter(padj < 0.01 & abs(log2FoldChange) > 2 & baseMean > 100)

```

### Subset the vsd keeping filtered elements 
```{r subset-vsd}
interval_subset <- top_days_comparisons$Intervals %>% unique()

# filter elements
vsd_hm <- count_vsd %>%
  filter(X %in% interval_subset) %>%
  column_to_rownames("X") %>%
  select(starts_with("WT"))

dim(vsd_hm)

```


### Restrict to changing in ALL domains

```{r filter-alldomains}

p1_elements <- Reduce(union, 
                       list(top_days_comparisons[top_days_comparisons$Comparison=="_p1__D5__D11_","Intervals"],
                     top_days_comparisons[top_days_comparisons$Comparison=="_p1__D5__D7_","Intervals"],
                     top_days_comparisons[top_days_comparisons$Comparison=="_p1__D5__D9_","Intervals"],
                     top_days_comparisons[top_days_comparisons$Comparison=="_p1__D7__D11_","Intervals"],
                     top_days_comparisons[top_days_comparisons$Comparison=="_p1__D7__D9_","Intervals"],
                     top_days_comparisons[top_days_comparisons$Comparison=="_p1__D9__D11_","Intervals"]))

p2_elements <- Reduce(union, 
                       list(top_days_comparisons[top_days_comparisons$Comparison=="_p2__D5__D11_","Intervals"],
                     top_days_comparisons[top_days_comparisons$Comparison=="_p2__D5__D7_","Intervals"],
                     top_days_comparisons[top_days_comparisons$Comparison=="_p2__D5__D9_","Intervals"],
                     top_days_comparisons[top_days_comparisons$Comparison=="_p2__D7__D11_","Intervals"],
                     top_days_comparisons[top_days_comparisons$Comparison=="_p2__D7__D9_","Intervals"],
                     top_days_comparisons[top_days_comparisons$Comparison=="_p2__D9__D11_","Intervals"]))

pM_elements <- Reduce(union, 
                       list(top_days_comparisons[top_days_comparisons$Comparison=="_pM__D5__D11_","Intervals"],
                     top_days_comparisons[top_days_comparisons$Comparison=="_pM__D5__D7_","Intervals"],
                     top_days_comparisons[top_days_comparisons$Comparison=="_pM__D5__D9_","Intervals"],
                     top_days_comparisons[top_days_comparisons$Comparison=="_pM__D7__D11_","Intervals"],
                     top_days_comparisons[top_days_comparisons$Comparison=="_pM__D7__D9_","Intervals"],
                     top_days_comparisons[top_days_comparisons$Comparison=="_pM__D9__D11_","Intervals"]))

length(p1_elements)
length(p2_elements)
length(pM_elements)


time_elements_allDomains <- Reduce(intersect, list(p1_elements,p2_elements,pM_elements))

str(time_elements_allDomains)

```



### Plot the elements in heatmap to visualize trends?

```{r plot-vsd-difftime}


# filter elements
vsd_hm <- count_vsd %>%
  filter(X %in% time_elements_allDomains) %>%
  column_to_rownames("X") %>%
  select(starts_with("WT"))

dim(vsd_hm)

# z score
vsd_hm_z <- t(scale(t(vsd_hm))) 

# metadata for the heatmap
genecolData_first <- data.frame(Sample_ID = colnames(vsd_hm))
genecolData_first <- genecolData_first %>% 
  separate(Sample_ID,into=c("Genotype","Day","Gate","NFIAgate","Rep"), sep="_", remove=FALSE) %>%
  mutate(Condition=paste(Genotype,Day,Gate,NFIAgate, sep="_"),
         DayNFIA=paste(Day,NFIAgate,Genotype,sep = "_"),
         DayGate=paste(Day,Gate,sep="_"),
         Experiment=paste(Genotype,Rep,sep="_"),
         NFIAstatus=paste(NFIAgate,Genotype,sep="_"))
genecolData_first <- as.data.frame(unclass(genecolData_first))

phen_data <- genecolData_first %>%
  select(c("Sample_ID","DayGate","Day","NFIAstatus","Rep")) %>%
  remove_rownames() %>%
  column_to_rownames("Sample_ID")

ann_color_JD <- list(
  DayGate = c(D5_p1="#abdff4",D5_p2="#f1df9a", D5_pM="#f19aac",
              D7_p1="#55bee8",D7_p2="#e6c444",D7_pM="#e64466",
              D9_p1="#1a91c1",D9_p2="#c19e1a",D9_pM="#c11a3d",
              D11_p1="#0e506b",D11_p2="#6b570e",D11_pM="#7c1127"),
  NFIAstatus = c(NFIAn_WT="#f6f6f6",NFIAp_WT="#cecece",`100`="#808080",NFIAn_MUT="#595959"),
  Day = c(D5="#fadede",D7="#f3aaaa",D9="#e96666",D11="#cf1e1e"),
  Rep = c(R1="#ebeb77", R2="#77b1eb", R3="#eb7777"))



# Annotated heatmap with selected colors
hm_colors = colorRampPalette(rev(brewer.pal(n = 11, name = "RdBu")))(100)


# Build the annotation for the complex heatmap
colAnn <- HeatmapAnnotation(
    df = phen_data,
    which = 'col', # 'col' (samples) or 'row' (gene) annotation?
    na_col = 'white', # default colour for any NA values in the annotation data-frame, 'ann'
    col = ann_color_JD,
    annotation_height = 0.6,
    annotation_width = unit(1, 'cm'),
    gap = unit(1, 'mm'))



hmap <- Heatmap(vsd_hm_z,

    name = 'Z-score',

    col = hm_colors,

    # row (gene) parameters
      cluster_rows = TRUE,
      show_row_dend = TRUE,
      #row_title = 'Statistically significant genes',
      row_title_side = 'left',
      row_title_gp = gpar(fontsize = 12,  fontface = 'bold'),
      row_title_rot = 90,
      show_row_names = FALSE,
      row_names_gp = gpar(fontsize = 10, fontface = 'bold'),
      row_names_side = 'left',
      row_dend_width = unit(25,'mm'),

    # column (sample) parameters
      cluster_columns = TRUE,
      show_column_dend = TRUE,
      column_title = '',
      column_title_side = 'bottom',
      column_title_gp = gpar(fontsize = 12, fontface = 'bold'),
      column_title_rot = 0,
      show_column_names = TRUE,
      column_names_gp = gpar(fontsize = 8),
      column_names_max_height = unit(10, 'cm'),
      column_dend_height = unit(25,'mm'),

    # cluster methods for rows and columns
      clustering_distance_columns = function(x) as.dist(1 - cor(t(x))),
      clustering_method_columns = 'ward.D2',
      clustering_distance_rows = function(x) as.dist(1 - cor(t(x))),
      clustering_method_rows = 'ward.D2',

    # specify top and bottom annotations
      top_annotation = colAnn)

```


```{r}

draw(hmap,
    heatmap_legend_side = 'left',
    annotation_legend_side = 'left',
    row_sub_title_side = 'left')

```


```{r mean-vsd-filtered}

vsd_elements_allDomains_ave <- vsd_hm %>%
  rownames_to_column("order") %>%
  gather(sample, vsd, starts_with("WT")) %>%
  mutate(condition = gsub('_R[1-3]', '', sample)) %>%
  group_by(order, condition) %>%
  summarise(ave_vsd = mean(vsd)) %>%
  spread(condition, ave_vsd) %>%
  ungroup() %>%
  column_to_rownames("order")

```



## kMeans clustering

```{r kmeans-clustering}

#x=1
choose_seed <- c(10,56,87,345,8,22)
#choose_seed = 10

lapply(c(1:length(choose_seed)), function(x){
  
  #set seed
  set.seed(choose_seed[x])
  ## kmeans
  vsd_kclusterd_2 <- kmeans(vsd_elements_allDomains_ave,30,iter.max = 100, nstart = 50)
  clustering_qc <- data.frame("Tot.withinss"=vsd_kclusterd_2$tot.withinss,
                              "ifault"=vsd_kclusterd_2$ifault)
  
  write.table(clustering_qc, file=paste0(workingdir,outdir,"Stats_30_iter_",x,".txt"), sep = "\t", quote = FALSE, row.names = FALSE)
  
  vsd_kclusterd <- vsd_kclusterd_2
  
  # get cluster centers to plot and get distances
  clusters_k30_plot <- vsd_kclusterd$centers %>% as.data.frame() %>%
    rownames_to_column("cluster") %>%
    gather(Sample,Centers, starts_with("WT")) %>%
    separate(Sample,into=c("Genotype","Day","Gate","NFIAgate"), sep="_", remove=FALSE) %>%
    mutate(Condition=paste(Genotype,Day,Gate,NFIAgate, sep="_"),
         DayNFIA=factor(paste(Day,NFIAgate,Genotype,sep = "_"), levels=sorted.dayNfia),
         NFIAstatus=paste(NFIAgate,Genotype,sep="_"),
         DayGate=factor(paste(Day,Gate,sep="_"), levels = sorted.DayGate),
         Day=factor(Day, levels = sorted.day), 
          Sample=factor(Sample, levels = sorted.sample))


# plot center per cluster
  plot_centers <- ggplot(clusters_k30_plot, aes(x=Sample,y=Centers, group=cluster))+
    geom_line() +
    geom_point(aes(color=DayGate)) +
    scale_color_manual(values = colorIZ) + 
    facet_wrap(~cluster, ncol = 5) +
    #facet_wrap(~cluster, ncol = 5, scales = "free_y") +
    theme_classic(base_size=8) +
    theme(axis.text.x = element_text(angle = 90, hjust = 1, size=6)) +
    theme(axis.title = element_text(size=10)) +
    theme(text=element_text(size=10))
  
  ggsave(paste0(workingdir,outdir,"Plots_30_Cluster_expression_Iter_",x,".pdf"), 
          width=8, height=8, units="in", useDingbats=FALSE)
  
  #plot_centers
# get cluster centers
  clusters_k30 <- vsd_kclusterd$centers
  write.table(clusters_k30, file=paste0(workingdir,outdir,"Cluster_30_Centers_iter_",x,".txt"), sep = "\t", quote = FALSE, row.names = FALSE)
  
  clusters_genes_k30 <- as.data.frame(vsd_kclusterd$cluster) %>%
    rownames_to_column()
  colnames(clusters_genes_k30) <- c("Peakid","Cluster")
# names(clusters_genes_k30)[1] <- "Geneid"
# names(clusters_genes_k30)[2] <- "Cluster"

  clusters_genes_k30 <- clusters_genes_k30[order(clusters_genes_k30[,2] ),]

  write.csv(clusters_genes_k30, file=paste0(workingdir,outdir,"Peaks_Cluster_30_Centers_iter_",x,".csv"), quote = FALSE, row.names = FALSE)
  
  ## Computing correlation based distances
  dist_cluster <- get_dist(clusters_k30, method = "pearson")
  dist_cluster_hm <- as.matrix(dist_cluster)
  
  #calculate hclust
  hcl=hclust(dist_cluster)
 
  ## chose the number of re-clusters here
  k=7
   
  # print hierchical cluster and cutree for each iteration
  pdf(paste0(workingdir,outdir,"Plot_",k,"hclust_Iter_",x,".pdf")) 

  plot(hcl, hang= -1) 
  reclusters <- rect.hclust(hcl, k, border = "red")
  
  dev.off() 


# visualize the re-clustering 
  # visualize the clusters and mega clusters
  ReClustering_dirty <- do.call(rbind.data.frame, reclusters)
  
  ReClustering <- ReClustering_dirty %>% rownames_to_column("ReCluster") %>% 
    gather("col_del", "cluster", 2:(ncol(ReClustering_dirty)+1)) %>%
    dplyr::select("cluster","ReCluster") %>%
    unique() %>%
    arrange(cluster) %>%
    remove_rownames() %>%
    column_to_rownames("cluster")
  
  #color clusters
  k=length(unique(ReClustering$ReCluster)) # how many clusters
  Nclusters <- c(1:k) %>% as.character() # make vector
  Ncolors <- colorRampPalette(brewer.pal(12, "Set3"))(k) # get colors

  
  names(Ncolors) <- Nclusters # named vector
  
  hm_colors = colorRampPalette(rev(brewer.pal(n = 11, name = "RdBu")))(100)
  
  ann_color_cluster <- list(
    ReCluster = c(Ncolors))
  
  # make Complex heatmap annotation 
  heatmap_ann_row <- rowAnnotation(df=ReClustering, col=ann_color_cluster)
  heatmap_ann <- HeatmapAnnotation(df=ReClustering, col=ann_color_cluster,
                                   show_legend = FALSE)
  
  
  
  # print hierchical cluster and cutree for each iteration
  pdf(paste0(workingdir,outdir,"Plot_",k,"_HeatmapReCluster_Iter_",x,".pdf"), width = 10, height = 9) 
  
  
  # now with colors of the reclustering
  draw(Heatmap(cor(t(clusters_k30)), name="Cluster cor", col=hm_colors,
          left_annotation = heatmap_ann_row, top_annotation = heatmap_ann,
          clustering_distance_columns = function(x) as.dist(1 - cor(t(x))),
          clustering_method_columns = 'complete',
          clustering_distance_rows = function(x) as.dist(1 - cor(t(x))),
          clustering_method_rows = 'complete',
          column_dend_height = unit(2, "cm"), row_dend_width = unit(2, "cm")))
  
  dev.off()
  

 # how to plot clusters in a heatmap
  pamClusters <- vsd_kclusterd$cluster %>% as.data.frame() %>%
    rename("cluster"=".") %>%
    rownames_to_column("order") %>%
    merge(ReClustering %>% rownames_to_column("cluster")) %>%
    arrange(order)
  write.csv(pamClusters, file = paste0(workingdir,outdir,"Output_",k,"_ReClusters_Iter_",x,".csv"), row.names = FALSE, quote = FALSE)
  
  ## plot zscores per ReCluster

  # scale the vsd data
  #heat <- t(scale(t(vsd_pairwise_ave)))
  # you already have this, it is called: vsd_subset_z_score
  
  # # how to plot clusters in a heatmap
  reclusteres_cluster_order <- vsd_kclusterd$cluster %>% as.data.frame() %>%
    rename("cluster"=".") %>%
    rownames_to_column("order") %>%
    merge(ReClustering %>% rownames_to_column("cluster")) %>%
    arrange(order)
  
  ## heatmap 1:  heatmap of genes with re-clusters annotated
  ### get the full dataset with all replicates 
  
  vsd_hm_z <- t(scale(t(vsd_hm))) 
  
genecolData_first <- data.frame(Sample_ID = colnames(vsd_hm))
genecolData_first <- genecolData_first %>% 
  separate(Sample_ID,into=c("Genotype","Day","Gate","NFIAgate","Rep"), sep="_", remove=FALSE) %>%
  mutate(Condition=paste(Genotype,Day,Gate,NFIAgate, sep="_"),
         DayNFIA=paste(Day,NFIAgate,Genotype,sep = "_"),
         DayGate=paste(Day,Gate,sep="_"),
         NFIAstatus=paste(NFIAgate,Genotype,sep="_"))
genecolData_first <- as.data.frame(unclass(genecolData_first))

phen_data <- genecolData_first %>%
  dplyr::select(c("Sample_ID","DayGate","Day","NFIAstatus","Rep")) %>%
  remove_rownames() %>%
  column_to_rownames("Sample_ID")
ann_color_IZ <- list(
  DayGate = c(D5_p1="#abdff4",D5_p2="#f1df9a", D5_pM="#f19aac",
              D7_p1="#55bee8",D7_p2="#e6c444",D7_pM="#e64466",
              D9_p1="#1a91c1",D9_p2="#c19e1a",D9_pM="#c11a3d",
              D11_p1="#0e506b",D11_p2="#6b570e",D11_pM="#7c1127"),
  NFIAstatus = c(NFIAn_WT="#f6f6f6",NFIAp_WT="#cecece",`100`="#808080",NFIAn_MUT="#595959"),
  Day = c(D5="#fadede",D7="#f3aaaa",D9="#e96666",D11="#cf1e1e"),
  Rep = c(R1="#ebeb77", R2="#77b1eb", R3="#eb7777"))


# Annotated heatmap with selected colors
hm_colors = colorRampPalette(rev(brewer.pal(n = 11, name = "RdBu")))(100)


# Build the annotation for the complex heatmap
colAnn <- HeatmapAnnotation(
    df = phen_data,
    which = 'col', # 'col' (samples) or 'row' (gene) annotation?
    na_col = 'white', # default colour for any NA values in the annotation data-frame, 'ann'
    col = ann_color_IZ,
    annotation_height = 0.6,
    annotation_width = unit(1, 'cm'),
    gap = unit(1, 'mm'))

# annotations Rows
phen_intervals <- vsd_hm_z %>%
  as.data.frame() %>%
  rownames_to_column("order") %>%
  left_join(reclusteres_cluster_order, by="order") %>%
  select(ReCluster)


#Ncolors <- colorRampPalette(brewer.pal(5, "Oranges"))(5)
# ann_colRows_JD <- list(
#     N_comparison =c(`1`="#FEEDDE",`2`="#FDBE85",`3`="#FD8D3C"),
#     Comp__p1__D7__D11_ =c(`1`="#377EB8"),
#     Comp__p2__D7__D11_=c(`1`="#4DAF4A"),
#     Comp__pM__D7__D11_=c(`1`="#E41A1C"))


rowAnn <- HeatmapAnnotation(
  which = 'row',
  df=phen_intervals,
  col = ann_color_cluster,
  na_col = 'white')

hmap <- Heatmap(vsd_hm_z,

    # split the genes / rows according to the PAM clusters
    #split = phen_intervals,
    # cluster_row_slices = FALSE,

    name = 'Z-score',
    row_km = k,

    col = hm_colors,

    # row (gene) parameters
      cluster_rows = TRUE,
      show_row_dend = TRUE,
      #row_title = 'Statistically significant genes',
      row_title_side = 'left',
      row_title_gp = gpar(fontsize = 12,  fontface = 'bold'),
      row_title_rot = 90,
      show_row_names = FALSE,
      row_names_gp = gpar(fontsize = 10, fontface = 'bold'),
      row_names_side = 'left',
      row_dend_width = unit(25,'mm'),

    # column (sample) parameters
      cluster_columns = TRUE,
      show_column_dend = TRUE,
      column_title = '',
      column_title_side = 'bottom',
      column_title_gp = gpar(fontsize = 12, fontface = 'bold'),
      column_title_rot = 0,
      show_column_names = TRUE,
      column_names_gp = gpar(fontsize = 8),
      column_names_max_height = unit(10, 'cm'),
      column_dend_height = unit(25,'mm'),

    # cluster methods for rows and columns
      clustering_distance_columns = function(x) as.dist(1 - cor(t(x))),
      clustering_method_columns = 'ward.D2',
      clustering_distance_rows = 'pearson',
      clustering_method_rows = 'single',

    # specify top and bottom annotations
      left_annotation = rowAnn,
      top_annotation = colAnn)

 # print hierchical cluster and cutree for each iteration
  pdf(paste0(workingdir,outdir,"Plot_",k,"_Heatmap_ReCluster_Iter_",x,".pdf"), width = 12, height = 9) 


draw(hmap,
    heatmap_legend_side = 'left',
    annotation_legend_side = 'left',
    row_sub_title_side = 'left')

dev.off()


## heatmap 2: Rows split by ReClusters 

hmap <- Heatmap(vsd_hm_z,

    # split the genes / rows according to the PAM clusters
    split = phen_intervals,
    # cluster_row_slices = FALSE,

    name = 'Z-score',

    col = hm_colors,

    # row (gene) parameters
      cluster_rows = TRUE,
      show_row_dend = TRUE,
      #row_title = 'Statistically significant genes',
      row_title_side = 'left',
      row_title_gp = gpar(fontsize = 12,  fontface = 'bold'),
      row_title_rot = 90,
      show_row_names = FALSE,
      row_names_gp = gpar(fontsize = 10, fontface = 'bold'),
      row_names_side = 'left',
      row_dend_width = unit(25,'mm'),

    # column (sample) parameters
      cluster_columns = TRUE,
      show_column_dend = TRUE,
      column_title = '',
      column_title_side = 'bottom',
      column_title_gp = gpar(fontsize = 12, fontface = 'bold'),
      column_title_rot = 0,
      show_column_names = TRUE,
      column_names_gp = gpar(fontsize = 8),
      column_names_max_height = unit(10, 'cm'),
      column_dend_height = unit(25,'mm'),

    # cluster methods for rows and columns
      clustering_distance_columns = function(x) as.dist(1 - cor(t(x))),
      clustering_method_columns = 'ward.D2',
      clustering_distance_rows = function(x) as.dist(1 - cor(t(x))),
      clustering_method_rows = 'ward.D2',

    # specify top and bottom annotations
      left_annotation = rowAnn,
      top_annotation = colAnn)

 # print hierchical cluster and cutree for each iteration
  pdf(paste0(workingdir,outdir,"Plot_",k,"_Heatmap_Split_ReCluster_Iter_",x,".pdf"), width = 12, height = 9) 


draw(hmap,
    heatmap_legend_side = 'left',
    annotation_legend_side = 'left',
    row_sub_title_side = 'left')

dev.off()


## get the number of elements per recluster for violin plot representation 
  
  n.hcluster <- reclusteres_cluster_order %>%
    group_by(ReCluster) %>%
    summarise(n = n()) %>%
    mutate(label = sprintf('n = %s', n))
   
  ## Violin   
  reclustered_hclust_zcoresconditions <- vsd_hm_z %>% as.data.frame() %>%
    rownames_to_column("order") %>%
    merge(reclusteres_cluster_order, by="order" ) %>%
    gather(Sample, Zscore, starts_with("WT")) %>%
    separate(Sample, into=c("Genotype","Day","Gate","NFIAgate"), sep="_", remove=FALSE) %>%
    mutate(Condition=paste(Genotype,Day,Gate,NFIAgate, sep="_"),
         DayNFIA=factor(paste(Day,NFIAgate,Genotype,sep = "_"), levels=sorted.dayNfia),
         NFIAstatus=paste(NFIAgate,Genotype,sep="_"),
         DayGate=factor(paste(Day,Gate,sep="_"), levels = sorted.DayGate),
         Day=factor(Day, levels = sorted.day), 
         Condition=factor(Condition, levels = sorted.sample))
  

zscore_plot <-  ggplot(reclustered_hclust_zcoresconditions, aes(x = Condition, y = Zscore, fill=DayGate)) + 
    geom_violin(size=0.2) +
    scale_fill_manual(values = colorIZ) +
    facet_wrap(~ReCluster) + xlab('') + ylab('Z-Score') +
    geom_text_repel(data = n.hcluster, aes(x = 0.75, y = 4, label = label), inherit.aes = F) +
    geom_hline(yintercept = 0, col = 'red', linetype = 'dashed') +
    theme_bw(base_size=10)+
    theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5),
          legend.position = 'none')

    ggsave(paste0(workingdir,outdir,"Plot_",k,"_ReCluster_Iter_",x,".pdf"), 
           width=10, height=5, units="in", useDingbats=FALSE)

#zscore_plot
  
    
})


```



```{r}
sessionInfo()
```