---
title: "ATAC_3_time_comparisons"
output: github_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

```

# ATAC analysis

Import elements that recapitulate the temporal program 

```{r message=FALSE}

rm(list=ls())

library(RColorBrewer)
library(tidyverse)
library(ComplexHeatmap)
library(Hmisc)
library(corrplot)

```


### Load settings

Colors, main directory 

```{r}

source('./r_inputs/TemporalSpatialNeuralTube_settings.R')

```

### Set dirs
```{r}

subworkinput="outputs_glialatac_2_time_clusters/"
subinputdir1="output_glialscATAC/"

# subinputdir2="output_Time_Specific/"

outdir="outputs_glialatac_3_time_comparisons/"
ifelse(!dir.exists(file.path(workingdir,outdir)), dir.create(file.path(workingdir,outdir)), "Directory exists")

```



## Load data

Load vsd to plot heatmaps later
```{r load-vsd}

count_vsd <- read.csv(file=paste0(workingdir,"outputs_glialatac_1/","consensus_peaks.mLb.vsd.csv"),header=TRUE, stringsAsFactors = FALSE)

temporal_program <- read.table(file = paste0(workingdir,subworkinput,"Intervals_temporal_Alldomains_cluster_and_interval_annotation.txt"), 
                               header = TRUE, sep="\t")

```

# filter elements to those in the temporal clusters 

```{r}
# filter elements
vsd_hm <- count_vsd %>%
  filter(X %in% temporal_program$order) %>%
  column_to_rownames("X") %>%
  select(starts_with("WT"))

dim(vsd_hm)

```



## Heatmap by clusters clustering

```{r heatmap-clustering}

# z score
vsd_hm_z <- t(scale(t(vsd_hm))) 


genecolData_first <- data.frame(Sample_ID = colnames(vsd_hm))
genecolData_first <- genecolData_first %>% 
  separate(Sample_ID,into=c("Genotype","Day","Gate","NFIAgate","Rep"), sep="_", remove=FALSE) %>%
  mutate(Condition=paste(Genotype,Day,Gate,NFIAgate, sep="_"),
         DayNFIA=paste(Day,NFIAgate,Genotype,sep = "_"),
         DayGate=paste(Day,Gate,sep="_"),
         NFIAstatus=paste(NFIAgate,Genotype,sep="_"))
genecolData_first <- as.data.frame(unclass(genecolData_first))

phen_data <- genecolData_first %>%
  dplyr::select(c("Sample_ID","DayGate","Day","NFIAstatus","Rep")) %>%
  remove_rownames() %>%
  column_to_rownames("Sample_ID")
ann_color_IZ <- list(
  DayGate = c(D5_p1="#abdff4",D5_p2="#f1df9a", D5_pM="#f19aac",
              D7_p1="#55bee8",D7_p2="#e6c444",D7_pM="#e64466",
              D9_p1="#1a91c1",D9_p2="#c19e1a",D9_pM="#c11a3d",
              D11_p1="#0e506b",D11_p2="#6b570e",D11_pM="#7c1127"),
  NFIAstatus = c(NFIAn_WT="#f6f6f6",NFIAp_WT="#cecece",`100`="#808080",NFIAn_MUT="#595959"),
  Day = c(D5="#fadede",D7="#f3aaaa",D9="#e96666",D11="#cf1e1e"),
  Rep = c(R1="#ebeb77", R2="#77b1eb", R3="#eb7777"))


# Annotated heatmap with selected colors
hm_colors = colorRampPalette(rev(brewer.pal(n = 11, name = "RdBu")))(100)


# Build the annotation for the complex heatmap
colAnn <- HeatmapAnnotation(
    df = phen_data,
    which = 'col', # 'col' (samples) or 'row' (gene) annotation?
    na_col = 'white', # default colour for any NA values in the annotation data-frame, 'ann'
    col = ann_color_IZ,
    annotation_height = 0.6,
    annotation_width = unit(1, 'cm'),
    gap = unit(1, 'mm'))

# annotations Rows
phen_intervals <- vsd_hm_z %>%
  as.data.frame() %>%
  rownames_to_column("order") %>%
  left_join(temporal_program, by="order") %>%
  select(Description)


#color clusters
  k=length(unique(temporal_program$ReCluster)) # how many clusters
  Nclusters <- c(1:k) %>% as.character() # make vector
  Ncolors <- colorRampPalette(brewer.pal(12, "Set3"))(k) # get colors
  
ann_color_cluster <- list(
    Description = c(Ncolors))

names(Ncolors) <- c("Late_3","Late_1","Late_2","Intermediate_1","Early_3",
                                           "Early_1","Early_2") # named vector

hm_colors = colorRampPalette(rev(brewer.pal(n = 11, name = "RdBu")))(100)
  
  ann_color_cluster <- list(
    Description = c(Ncolors))

rowAnn <- HeatmapAnnotation(
  which = 'row',
  df=phen_intervals,
  col = ann_color_cluster,
  na_col = 'white')




```

```{r fig.height=8, fig.width=9}
set.seed(8)

hmap <- Heatmap(vsd_hm_z,

    # split the genes / rows according to the PAM clusters
    row_split = phen_intervals,
    row_title = "cluster_%s",
    row_title_rot = 0,
    cluster_row_slices = FALSE, 
    #cluster_column_slices = FALSE,
    

    name = 'Z-score',

    col = hm_colors,

    # row (gene) parameters
      cluster_rows = TRUE,
      show_row_dend = TRUE,
      #row_title = 'Statistically significant genes',
      row_title_side = 'left',
      row_title_gp = gpar(fontsize = 12,  fontface = 'bold'),
      #row_title_rot = 90,
      show_row_names = FALSE,
      row_names_gp = gpar(fontsize = 10, fontface = 'bold'),
      row_names_side = 'left',
      row_dend_width = unit(25,'mm'),

    # column (sample) parameters
      cluster_columns = TRUE,
      show_column_dend = TRUE,
      column_title = '',
      column_title_side = 'bottom',
      column_title_gp = gpar(fontsize = 12, fontface = 'bold'),
      column_title_rot = 0,
      show_column_names = TRUE,
      column_names_gp = gpar(fontsize = 8),
      column_names_max_height = unit(10, 'cm'),
      column_dend_height = unit(25,'mm'),

    # cluster methods for rows and columns
      clustering_distance_columns = function(x) as.dist(1 - cor(t(x))),
      clustering_method_columns = 'ward.D2',
      clustering_distance_rows = function(x) as.dist(1 - cor(t(x))),
      clustering_method_rows = 'ward.D2',

    # specify top and bottom annotations
      left_annotation = rowAnn,
      top_annotation = colAnn)

```


```{r fig.height=8, fig.width=9}

draw(hmap,
    heatmap_legend_side = 'left',
    annotation_legend_side = 'left',
    row_sub_title_side = 'left')


```


Can I extract the order - this is just to double check the scATAC export

```{r}

# r.dend <- row_dend(hmap)  #Extract row dendrogram
# rcl.list <- row_order(hmap)  #Extract clusters (output is a list)
# 
# lapply(rcl.list, function(x) length(x))  #check/confirm size clusters
# 
# # loop to extract genes for each cluster.
# for (i in 1:length(row_order(hmap))){
#  if (i == 1) {
#  clu <- t(t(row.names(vsd_hm_z[row_order(hmap)[[i]],])))
#  out <- cbind(clu, paste("cluster", i, sep=""))
#  colnames(out) <- c("GeneID", "Cluster")
#  } else {
#  clu <- t(t(row.names(vsd_hm_z[row_order(hmap)[[i]],])))
#  clu <- cbind(clu, paste("cluster", i, sep=""))
#  out <- rbind(out, clu)
#  }
#  }
# 
# gene_clusters <- as.data.frame(out)
# 
# write.csv(gene_clusters,paste0(workingdir,outdir,"elements_in_order.csv"),quote = FALSE, row.names = FALSE)

```

### Prep the vsd from in vitro

```{r}

vsd_hm_ave <- vsd_hm %>% 
  rownames_to_column("order") %>%
  pivot_longer(starts_with("WT"), names_to = "Sample_ID",values_to = "vsd") %>%
  separate(Sample_ID,into=c("Genotype","Day","Gate","NFIAgate","Rep"), sep="_", remove=FALSE) %>%
  mutate(Condition=paste(Genotype,Day,Gate,NFIAgate, sep="_"),
         DayNFIA=paste(Day,NFIAgate,Genotype,sep = "_"),
         DayGate=paste(Day,Gate,sep="_"),
         NFIAstatus=paste(NFIAgate,Genotype,sep="_")) %>%
  group_by(Day,order) %>%
  summarise(vsd_ave = mean(vsd)) %>%
  ungroup() %>% 
  pivot_wider(values_from = "vsd_ave", names_from = "Day") %>%
  select(order,D5,D7,D9,D11)

```


### Comparison: cerebellum

```{r}
cerebellum <- read.table(paste0(workingdir,subinputdir1,"cerebellum_temporalelements.txt"), header = TRUE)


```



```{r}

cerebellum_combined <-  vsd_hm_ave %>%
  left_join(cerebellum %>% dplyr::select(e10:e15, order), by="order") %>%
  column_to_rownames("order")

res <- cor(cerebellum_combined)

round(res, 2)

```

```{r}
res2 <- rcorr(as.matrix(cerebellum_combined), type="pearson")

```

```{r}


corrplot(res, type = "upper", 
         tl.col = "black", tl.srt = 45)

diag(res2$P) <- 0

# Insignificant correlation are crossed
corrplot(res2$r, type="upper", method = "color",tl.col = "black", tl.srt = 45,
         p.mat = res2$P, sig.level = 0.01, insig = "blank", pch.cex = 0.8, addCoef.col = 'black')

corrplot(res2$r, type="upper",tl.col = "black", tl.srt = 45,
         p.mat = res2$P, sig.level = 0.01, insig = "pch", pch.cex = 1)

corrplot(res2$r, type="upper",  tl.col = "black", tl.srt = 45,
         p.mat = res2$P, sig.level = 0.01, insig = "blank")

```
```{r }

# corrplot(res2$r[6:9,1:5], type="upper",tl.col = "black", tl.srt = 45, method = "color",
#          p.mat = res2$P[6:9,1:5], sig.level = 0.01, insig = "pch", pch.cex = 1, addCoef.col = 'black')


corrplot(res2$r[1:4,], type="upper",tl.col = "black", tl.srt = 45,
         p.mat = res2$P[1:4,], sig.level = 0.01, insig = "label_sig", pch.cex = 1, col = rev(COL2('RdBu', 10)))


```

### Comparison: cortex

```{r}
cortex <- read.table(paste0(workingdir,subinputdir1,"cortex_temporalelements.txt"), header = TRUE)


```



```{r}

cortex_combined <-  vsd_hm_ave %>%
  left_join(cortex %>% dplyr::select(e13_5:e18_5, order), by="order") %>%
  column_to_rownames("order")

res <- cor(cortex_combined)

round(res, 2)

```

```{r}
res2 <- rcorr(as.matrix(cortex_combined), type="pearson")

```

```{r}


corrplot(res, type = "upper", 
         tl.col = "black", tl.srt = 45)

diag(res2$P) <- 0

# Insignificant correlation are crossed
corrplot(res2$r, type="upper", method = "color",tl.col = "black", tl.srt = 45,
         p.mat = res2$P, sig.level = 0.01, insig = "blank", pch.cex = 0.8, addCoef.col = 'black')

corrplot(res2$r, type="upper",tl.col = "black", tl.srt = 45,
         p.mat = res2$P, sig.level = 0.01, insig = "pch", pch.cex = 1)

corrplot(res2$r, type="upper",  tl.col = "black", tl.srt = 45,
         p.mat = res2$P, sig.level = 0.01, insig = "blank")

```

```{r }

# corrplot(res2$r[6:9,1:5], type="upper",tl.col = "black", tl.srt = 45, method = "color",
#          p.mat = res2$P[6:9,1:5], sig.level = 0.01, insig = "pch", pch.cex = 1, addCoef.col = 'black')


corrplot(res2$r[1:4,], type="upper",tl.col = "black", tl.srt = 45,
         p.mat = res2$P[1:4,], sig.level = 0.01, insig = "label_sig", pch.cex = 1, col = rev(COL2('RdBu', 10)))


```

### Comparison: retina

```{r}
retina <- read.table(paste0(workingdir,subinputdir1,"retina_temporalelements.txt"), header = TRUE)


```



```{r}

retina_combined <-  vsd_hm_ave %>%
  left_join(retina %>% dplyr::select(e11:e18, order), by="order") %>%
  column_to_rownames("order")

res <- cor(retina_combined)

round(res, 2)

```

```{r}
res2 <- rcorr(as.matrix(retina_combined), type="pearson")

```

```{r}


corrplot(res, type = "upper", 
         tl.col = "black", tl.srt = 45)

diag(res2$P) <- 0

# Insignificant correlation are crossed
corrplot(res2$r, type="upper", method = "color",tl.col = "black", tl.srt = 45,
         p.mat = res2$P, sig.level = 0.01, insig = "blank", pch.cex = 0.8, addCoef.col = 'black')

corrplot(res2$r, type="upper",tl.col = "black", tl.srt = 45,
         p.mat = res2$P, sig.level = 0.01, insig = "pch", pch.cex = 1)

corrplot(res2$r, type="upper",  tl.col = "black", tl.srt = 45,
         p.mat = res2$P, sig.level = 0.01, insig = "blank")

```

```{r }

# corrplot(res2$r[6:9,1:5], type="upper",tl.col = "black", tl.srt = 45, method = "color",
#          p.mat = res2$P[6:9,1:5], sig.level = 0.01, insig = "pch", pch.cex = 1, addCoef.col = 'black')


corrplot(res2$r[1:4,], type="upper",tl.col = "black", tl.srt = 45,
         p.mat = res2$P[1:4,], sig.level = 0.01, insig = "label_sig", pch.cex = 1, col = rev(COL2('RdBu', 10)))


```

### Comparison: organogenesis atlas

```{r}
organogenesis <- read.table(paste0(workingdir,subinputdir1,"organo_temporalelements.txt"), header = TRUE)
organogenesis_sc <- read.table(paste0(workingdir,subinputdir1,"organoSC_temporalelements.txt"), header = TRUE)

  

```



```{r}

organogenesis0 <-  vsd_hm_ave %>%
  left_join(organogenesis_sc %>% dplyr::select(E10.5:E13.5, order), by="order") %>%
  column_to_rownames("order")

res2 <- rcorr(as.matrix(organogenesis0), type="pearson")
diag(res2$P) <- 0


# Insignificant correlation are crossed
corrplot(res2$r, type="upper", method = "color",tl.col = "black", tl.srt = 45,
         p.mat = res2$P, sig.level = 0.01, insig = "blank", pch.cex = 0.8, addCoef.col = 'black')

corrplot(res2$r[1:4,], type="upper",tl.col = "black", tl.srt = 45,
         p.mat = res2$P[1:4,], sig.level = 0.01, insig = "label_sig", pch.cex = 1, col = rev(COL2('RdBu', 10)))

```


```{r}

organogenesis1 <-  vsd_hm_ave %>%
  left_join(organogenesis %>% dplyr::select(ends_with("Hindbrain"), order), by="order") %>%
  column_to_rownames("order")

res2 <- rcorr(as.matrix(organogenesis1), type="pearson")
diag(res2$P) <- 0


# Insignificant correlation are crossed
corrplot(res2$r, type="upper", method = "color",tl.col = "black", tl.srt = 45,
         p.mat = res2$P, sig.level = 0.01, insig = "blank", pch.cex = 0.8, addCoef.col = 'black')

corrplot(res2$r[1:4,], type="upper",tl.col = "black", tl.srt = 45,
         p.mat = res2$P[1:4,], sig.level = 0.01, insig = "label_sig", pch.cex = 1, col = rev(COL2('RdBu', 10)))

```


```{r}

organogenesis2 <-  vsd_hm_ave %>%
  left_join(organogenesis %>% dplyr::select(ends_with("MHB"), order), by="order") %>%
  column_to_rownames("order")

res2 <- rcorr(as.matrix(organogenesis2), type="pearson")
diag(res2$P) <- 0


# Insignificant correlation are crossed
corrplot(res2$r, type="upper", method = "color",tl.col = "black", tl.srt = 45,
         p.mat = res2$P, sig.level = 0.01, insig = "blank", pch.cex = 0.8, addCoef.col = 'black')

corrplot(res2$r[1:4,], type="upper",tl.col = "black", tl.srt = 45,
         p.mat = res2$P[1:4,], sig.level = 0.01, insig = "label_sig", pch.cex = 1, col = rev(COL2('RdBu', 10)))

```

```{r}

organogenesis3 <-  vsd_hm_ave %>%
  left_join(organogenesis %>% dplyr::select(ends_with("telencephalon"), order), by="order") %>%
  column_to_rownames("order")

res2 <- rcorr(as.matrix(organogenesis3), type="pearson")
diag(res2$P) <- 0


# Insignificant correlation are crossed
corrplot(res2$r, type="upper", method = "color",tl.col = "black", tl.srt = 45,
         p.mat = res2$P, sig.level = 0.01, insig = "blank", pch.cex = 0.8, addCoef.col = 'black')

corrplot(res2$r[1:4,], type="upper",tl.col = "black", tl.srt = 45,
         p.mat = res2$P[1:4,], sig.level = 0.01, insig = "label_sig", pch.cex = 1, col = rev(COL2('RdBu', 10)))

```


### Comparison: Spinal Cord in vivo

```{r}

spinalcord <- read.table(paste0(workingdir,subinputdir1,"spinalcord_temporalelements.txt"), header = TRUE)

```



```{r}

spinalcord_combined <-  vsd_hm_ave %>%
  left_join(spinalcord %>% dplyr::select(e9_5,e10_5,e12_5,e13_5, order), by="order") %>%
  column_to_rownames("order")

res2 <- rcorr(as.matrix(spinalcord_combined), type="pearson")
diag(res2$P) <- 0


# Insignificant correlation are crossed
corrplot(res2$r, type="upper", method = "color",tl.col = "black", tl.srt = 45,
         p.mat = res2$P, sig.level = 0.01, insig = "blank", pch.cex = 0.8, addCoef.col = 'black')

corrplot(res2$r[1:4,], type="upper",tl.col = "black", tl.srt = 45,
         p.mat = res2$P[1:4,], sig.level = 0.01, insig = "label_sig", pch.cex = 1, col = rev(COL2('RdBu', 10)))

```

```{r}
sessionInfo()
```