---
title: "RNA_NFIAB_KO"
output: github_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

```

# RNA analysis
Differential gene exp in groups of samples: genes changing over time, and defects in NIFA/B KO. 

Generate the comparison and export the data. 

Start the analysis in the next script by importing these data so it is more efficient. 

```{r message=FALSE}

rm(list=ls())

library(DESeq2)
library(RColorBrewer)
library(tidyverse)
library(ComplexHeatmap)
library(tximport)
library(UpSetR)

```

### Load settings

Colors, main directory 

```{r}
source('./r_inputs/TemporalSpatialNeuralTube_settings.R')
```


### Set dirs
```{r}
outdir="outputs_NFIAB_RNA/"
#outdir="outputs_glialRNA_3_NFIAB_KO/"
subworkinput="inputs_glialRNA_1_qc/"
ifelse(!dir.exists(file.path(workingdir,outdir)), dir.create(file.path(workingdir,outdir)), "Directory exists")

suboutdir1="output_WT_KO_D7_D11/"
ifelse(!dir.exists(file.path(workingdir,outdir,suboutdir1)), dir.create(file.path(workingdir,outdir,suboutdir1)), "Directory exists")


```



## Load data

For RNA analysis, we are using the output of star_salmon so the import to deseq is a bit more complicated.

```{r }

#salmon counts from pipeline, import
path_files =  list.files(paste0(workingdir,subworkinput)) 
samples = data.frame(run=path_files, stringsAsFactors = FALSE) %>%
  filter(str_detect(run, "MUT|WT"))

files <- file.path(paste0(workingdir,subworkinput), samples$run, "quant.sf")
names(files) <- samples$run
all(file.exists(files))

#from pipeline
tx2gene = read_tsv(paste0(paste0(workingdir,subworkinput),"/salmon_tx2gene.tsv"))

txi.salmon <- tximport(files, type = "salmon", tx2gene = tx2gene)

```



## Differential analysis between WT and KO for each domain at two timepoints

Targeted diff analysis in subsets of samples:

Just for D7 and D11:
WT vs KO: pairwise for p1, p2, pMN
WT vs KO: pairwise for p1, p2, pMN

This DESeq2 analysis is done by subsetting samples. I subset the `txi.salmon$counts` table and then use ` DESeqDataSetFromMatrix` with `round(sub_counts)` to perform the differential analysis. 

```{r diff-KO-WT, message=FALSE, warnings=FALSE}

count_table <- txi.salmon$counts

count_matrix <- count_table %>%
  as.data.frame() %>%
  rownames_to_column("GeneID") %>%
  filter(!str_starts(GeneID, "ERCC")) %>%
  column_to_rownames("GeneID")

#subset 
timepoint=c("_D7_","_D11_")
#subset 
allgates=c("_p2_","_pM_","_p1_")

#no filtering based on genotype

comparisons <- allgates



PairWiseDEseq <- lapply(c(1:length(timepoint)),function (x) {
  lapply(c(1:length(allgates)), function (y) {
      timepoints <- timepoint[x]
      celltypes <- allgates[y]
      sub_counts <- count_matrix %>%
        dplyr::select(contains(celltypes) & contains(timepoints))
      
      ## Make metadata file for DESeq
      genecolData_sub <- data.frame(Sample_ID = colnames(sub_counts))
      genecolData_sub <- genecolData_sub %>% 
        separate(Sample_ID,into=c("Genotype","Day","Gate","NFIAgate","Rep"), sep="_", remove=FALSE) %>%
        mutate(Condition=paste(Genotype,Day,Gate,NFIAgate, sep="_"),
         DayNFIA=paste(Day,NFIAgate,Genotype,sep = "_"),
         DayGate=paste(Day,Gate,sep="_"),
         Experiment=paste(Genotype,Rep,sep="_"),
         NFIAstatus=paste(NFIAgate,Genotype,sep="_"))
      genecolData_sub <- as.data.frame(unclass(genecolData_sub))
      
      dds_sub <- DESeqDataSetFromMatrix(countData =  round(sub_counts),
                                    colData = genecolData_sub,
                                    design = ~ Genotype)
      
      dds_sub <- DESeq(dds_sub)
      
      vsd_sub <- varianceStabilizingTransformation(dds_sub,blind = FALSE)
      
      # Export normalized tables for plotting elsewhere
      dds_sub_counts <- counts(dds_sub, normalized = TRUE)
      vsd_sub_data <- assay(vsd_sub)
      
      results_sub <- results(dds_sub)

      results_return <- results_sub %>% as.data.frame() %>% rownames_to_column("Geneid")
      results_return$Comparison <- paste0(resultsNames(dds_sub)[2],timepoints,celltypes)
      results_return$Comparison <- gsub("Genotype","",results_return$Comparison)
      results_return

  })
}) 


```

### RNA: How many diff expressed genes between WT and KO?

```{r rna-filter-KO}

PairWiseDEseq_list <- unlist(PairWiseDEseq, recursive = FALSE)
results_deseq_nfia_rna <- do.call(rbind,PairWiseDEseq_list)


fc_cut <- 1
mean_cut <- 80

top_KO_comparisons_rna <- results_deseq_nfia_rna %>%
  as.data.frame() %>%
  filter(padj < 0.01 & abs(log2FoldChange) > fc_cut & baseMean > mean_cut) 

top_KO_comparisons_count_rna <- results_deseq_nfia_rna %>%
  as.data.frame() %>%
  filter(padj < 0.01 & abs(log2FoldChange) > fc_cut & baseMean > mean_cut) %>%
  mutate(Comparison=factor(Comparison, levels=results_deseq_nfia_rna$Comparison %>% unique())) %>%
  group_by(Comparison) %>% dplyr::count(Comparison,.drop=FALSE)

ggplot(top_KO_comparisons_count_rna, aes(x=Comparison,y=n)) +
  geom_col() +
  geom_point(color="black", fill="grey",shape=21) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))


```


### Are they the same ones? upset

```{r RNA-KO-overlap}

comparison_vector <- top_KO_comparisons_rna$Comparison %>% unique()

list_rna <- lapply(comparison_vector, function(x) {
  top_KO_comparisons_rna[top_KO_comparisons_rna$Comparison==x,"Geneid"]
})
names(list_rna) <- comparison_vector

#upset(fromList(list_test), sets=comparison_vector, order.by = "degree")
upset(fromList(list_rna), sets=comparison_vector, order.by = "freq")

```

```{r}

top_KO_comparisons_rna_d11 <- top_KO_comparisons_rna[str_detect(top_KO_comparisons_rna$Comparison, "_D11__"),"Comparison"] %>% unique()

list_rna_d11 <- lapply(top_KO_comparisons_rna_d11, function(x) {
  top_KO_comparisons_rna[top_KO_comparisons_rna$Comparison==x,"Geneid"]
})
names(list_rna_d11) <- top_KO_comparisons_rna_d11

upset(fromList(list_rna_d11), sets=top_KO_comparisons_rna_d11, order.by = "freq")

```


### Fig: Stacked bars

```{r}


rna_d11 <- fromList(list_rna_d11)

rna_d11_shaped <- rna_d11 %>%
  mutate(overlap_category=case_when( `_WT_vs_MUT_D11__p1_`=="1" & `_WT_vs_MUT_D11__p2_`=="0" & `_WT_vs_MUT_D11__pM_`=="0" ~ "p1",
                                     `_WT_vs_MUT_D11__p1_`=="0" & `_WT_vs_MUT_D11__p2_`=="1" & `_WT_vs_MUT_D11__pM_`=="0" ~ "p2",
                                     `_WT_vs_MUT_D11__p1_`=="0" & `_WT_vs_MUT_D11__p2_`=="0" & `_WT_vs_MUT_D11__pM_`=="1" ~ "pM",
                                     `_WT_vs_MUT_D11__p1_`=="1" & `_WT_vs_MUT_D11__p2_`=="1" & `_WT_vs_MUT_D11__pM_`=="1" ~ "all",
                                     `_WT_vs_MUT_D11__p1_`=="1" & `_WT_vs_MUT_D11__p2_`=="1" & `_WT_vs_MUT_D11__pM_`=="0" ~ "p1_p2",
                                     `_WT_vs_MUT_D11__p1_`=="0" & `_WT_vs_MUT_D11__p2_`=="1" & `_WT_vs_MUT_D11__pM_`=="1" ~ "p2_pM",
                                     `_WT_vs_MUT_D11__p1_`=="1" & `_WT_vs_MUT_D11__p2_`=="0" & `_WT_vs_MUT_D11__pM_`=="1" ~ "p1_pM",
                                     TRUE ~ "error")) %>%
  mutate(modality="rna") %>%
  mutate(overlap_category=factor(overlap_category, levels=rev(c("all","p2_pM","p1_p2","p1_pM","pM","p2","p1")))) %>%
  dplyr::select(overlap_category,modality)

           
```

```{r fig.width=3.5, fig.height=3}

bar_KO_atac_RNA <- ggplot(rna_d11_shaped, aes(x=modality)) + 
                      geom_bar(aes(fill=overlap_category), position = "fill") +
                      scale_fill_manual(values = rev(c("#4f4f4f","#8a8a8a","#c5c5c5","#d8d8d8","#c11a3d","#c19e1a","#1a91c1"))) +
                      ylab("Proportion of elements/genes") +
                      theme_minimal()

ggsave(plot=bar_KO_atac_RNA, filename=paste0(workingdir,outdir,"BarStacked_KO_ATAC_RNA.pdf"), device = "pdf",
             width=3.5, height=3, units="in", useDingbats=FALSE)


bar_KO_atac_RNA

```


### Print gene lists

Nfia/b dependent (d11), and cell type specific 

```{r}

NfiabKO_pMN_only <- data.frame(
  celltype = "pMN_specific",
  genenames = setdiff(list_rna_d11$`_WT_vs_MUT_D11__pM_`,union(list_rna_d11$`_WT_vs_MUT_D11__p2_`, list_rna_d11$`_WT_vs_MUT_D11__p1_`)))


NfiabKO_p2_only <- data.frame(
  celltype = "p2_specific",
  genenames = setdiff(list_rna_d11$`_WT_vs_MUT_D11__p2_`,union(list_rna_d11$`_WT_vs_MUT_D11__pM_`, list_rna_d11$`_WT_vs_MUT_D11__p1_`)))

NfiabKO_p1_only <- data.frame(
  celltype = "p1_specific",
  genenames = setdiff( list_rna_d11$`_WT_vs_MUT_D11__p1_`,union(list_rna_d11$`_WT_vs_MUT_D11__pM_`, list_rna_d11$`_WT_vs_MUT_D11__p2_`)))

NfiabKO_celltypespecific <- do.call(rbind, list(NfiabKO_pMN_only,NfiabKO_p2_only,NfiabKO_p1_only))


write.csv(NfiabKO_celltypespecific, file =paste0(workingdir,outdir,"NFIAB_dependent_genes_celltypespecific.csv"), row.names = FALSE,
          quote = FALSE )

```




```{r}
sessionInfo()
```