---
title: "ATAC_2_time_vs_domain_import"
output: github_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

```

# ATAC analysis
Differential accessibility in groups of samples

Imports diff accessibility and plots numbers of elements changing in time and space. Export tables.

```{r message=FALSE}

rm(list=ls())

library(DESeq2)
library(RColorBrewer)
library(tidyverse)
library(ComplexHeatmap)
library(UpSetR)

```


### Load settings

Colors, main directory 

```{r}

source('./r_inputs/TemporalSpatialNeuralTube_settings.R')

```

### Set dirs
```{r}

subworkinput="outputs_glialatac_2_time_space/"

suboutdir1="output_Domain_Specific/"
suboutdir2="output_Time_Specific/"


```



## Load data

Load the diff expression from previous script. 

## Differential analysis between domains for each timepoint

Targeted diff analysis in subsets of samples:

Wild type only:
D5: pairwise for p1, p2, pMN
D7: pairwise for p1, p2, pMN
D9: pairwise for p1, p2, pMN
D11: pairwise for p1, p2, pMN


re importing does not work because the ~/ gets converted to full name of the dir

Change working dir to local and it'll be fine. For not, this is the patch. 

```{r  import-domain}

PairWiseDEseq_domain <- lapply(list.files(path=paste0(workingdir,subworkinput,suboutdir1),pattern="Results_DESeq*", full.names=TRUE),function(x) {
  data <- read.table(x,header=T,stringsAsFactors=F) %>% as.data.frame() %>% rownames_to_column("Intervals")
  data$Comparison <- gsub(paste0(workingdir,subworkinput,suboutdir1,"/Results_DESeq_"),"", x)
  data$Comparison <- gsub(".txt","",data$Comparison)
  data
})

results_deseq_domain <- do.call(rbind,PairWiseDEseq_domain)

```
## Differential analysis between timepoints for each domain

Targeted diff analysis in subsets of samples:

Wild type only:
p1: pairwise D5-D7, D7-D9, D9-D11, D5-D9, D5-D11, D7-D11
p2: pairwise D5-D7, D7-D9, D9-D11, D5-D9, D5-D11, D7-D11
pM: pairwise D5-D7, D7-D9, D9-D11, D5-D9, D5-D11, D7-D11

```{r}

PairWiseDEseq_days <- lapply(list.files(path=paste0(workingdir,subworkinput,suboutdir2),pattern="Results_DESeq*", full.names=TRUE),function(x) {
  data <- read.table(x,header=T,stringsAsFactors=F) %>% as.data.frame() %>% rownames_to_column("Intervals")
  data$Comparison <- gsub(paste0(workingdir,subworkinput,suboutdir2,"/Results_DESeq_"),"", x)
  data$Comparison <- gsub(".txt","",data$Comparison)
  data
})

results_deseq_days <- do.call(rbind,PairWiseDEseq_days)

```


### How many diff acc elements between domains?

```{r filter-gates}

top_domain_comparisons <- results_deseq_domain %>%
  as.data.frame() %>%
  filter(padj < 0.01 & abs(log2FoldChange) > 2 & baseMean > 100)

```


### How many diff acc elements between timepoints?

```{r filter-days}

top_days_comparisons <- results_deseq_days %>%
  as.data.frame() %>%
  filter(padj < 0.01 & abs(log2FoldChange) > 2 & baseMean > 100)

```


## Plot number of elements changing between domains and over time

```{r plot-fig-numbers, fig.width=8.5, fig.height=3}

top_combined_comparisons <- rbind(top_days_comparisons,top_domain_comparisons)

#tidy
top_combined_comparisons <- top_combined_comparisons %>%
  separate(Comparison, into = c("empty","faceting","dimension","dim1","vs","dim2"), sep = "_")  %>%
  mutate(dim2=factor(dim2, levels=c("D11","D7","D5","p2","p1")),
         dim1=factor(dim1, levels=c("p2","pM","D5","D7","D9")))

ggplot(top_combined_comparisons, aes(x=dim1, y=dim2)) +
  geom_count(aes(color=dimension)) +
  scale_colour_brewer(palette = "Set1") +
  scale_size(range = c(1,9), breaks = seq(0,10000, by=1000)) + 
  facet_grid(dimension ~ faceting, scales = "free") +
  theme_bw()

```



```{r}
sessionInfo()
```